%%%%%%%%%%%%%%%%%%%%%%%% referenc.tex %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% sample references
% %
% Use this file as a template for your own input.
%
%%%%%%%%%%%%%%%%%%%%%%%% Springer-Verlag %%%%%%%%%%%%%%%%%%%%%%%%%%
%
% BibTeX users please use
% \bibliographystyle{}
% \bibliography{}
%

\begin{thebibliography}{99.}%
% and use \bibitem to create references.
%
% Use the following syntax and markup for your references if 
% the subject of your book is from the field 
% "Mathematics, Physics, Statistics, Computer Science"
%
% Contribution 

\bibitem{psysoc-journal} Mitani, Y., Ino, F. and Hagihara, K., 2017. Parallelizing exact and approximate string matching via inclusive scan on a GPU. \textit{IEEE Transactions on Parallel and Distributed Systems}, 28(7), pp.1989-2002 
\bibitem{psysoc-journal} Agrawal, J., Diao, Y., Gyllstrom, D. and Immerman, N., 2008, June. Efficient pattern matching over event streams. In \textit{Proceedings of the 2008 ACM SIGMOD international conference on Management of data} (pp. 147-160). ACM.
%
\bibitem{psysoc-journal} Cantone, D., Cristofaro, S. and Faro, S., 2010, August. A Space-Efficient Implementation of the Good-Suffix Heuristic. In \textit{Stringology} (pp. 63-75).
%
% Journal article by DOI
\bibitem{psysoc-DOI}Sahli, M. and Shibuya, T., 2012. Max-shift BM and max-shift horspool: Practical fast exact string matching algorithms. \textit{Journal of information processing}, 20(2), pp.419-425.

\bibitem{psysoc-DOI}Park, B. and Won, C.S., 2014, June. Fast binary matching for edge histogram descriptor. In \textit{Consumer Electronics (ISCE 2014), The 18th IEEE International Symposium} (pp. 1-2).
\bibitem{psysoc-DOI}Hirvola, T. and Tarhio, J., 2017. Bit-Parallel Approximate Matching of Circular Strings with k Mismatches. \textit{Journal of Experimental Algorithmics (JEA)}, 22, pp.1-5.
\bibitem{psysoc-DOI}Pfaffe, P., Tillmann, M., Lutteropp, S., Scheirle, B. and Zerr, K., 2016, August. Parallel String Matching. In \textit{European Conference on Parallel Processing} (pp. 187-198). Springer, Cham.
\bibitem{psysoc-DOI}Faro, S., 2016, June. Evaluation and improvement of fast algorithms for exact matching on genome sequences. In \textit{International Conference on Algorithms for Computational Biology} (pp. 145-157). Springer, Cham.
\bibitem{psysoc-DOI}Oladunjoye, J.A., Afolabi, A.O., Olabiyisi, S.O. and Moses, T., 2017. A Comparative Analysis of Pattern Matching Algorithm Using Bit-Parallelism Technique. \textit{IUP Journal of Information Technology}, 13(4), pp.20-36.

\bibitem{psysoc-DOI}Fredriksson, K., 2003. Shift-or string matching with super-alphabets. Information Processing Letters, 87(4), pp.201-204.
\bibitem{psysoc-DOI}Kida, T., Takeda, M., Shinohara, A. and Arikawa, S., 1999, July. Shift-And approach to pattern matching in LZW compressed text. In \textit{Annual Symposium on Combinatorial Pattern Matching (pp. 1-13)}. Springer, Berlin, Heidelberg.
\bibitem{psysoc-DOI}Goyal, R. and Billa, S.L., Cavium Inc, 2017. Generating a non-deterministic finite automata (NFA) graph for regular expression patterns with advanced features. U.S. Patent
9,563,399.

\bibitem{psysoc-DOI}Hirvola, T. and Tarhio, J., 2017. Bit-Parallel Approximate Matching of Circular Strings with k Mismatches. \textit{Journal of Experimental Algorithmics (JEA)}, 22, pp.1-5.

\bibitem{psysoc-DOI}Alfred, V., 2014. Algorithms for finding patterns in strings. Algorithms and Complexity,p.255, pp.1-5.

\end{thebibliography}
